### 2019-01-16 Sections/economics_of_the_quantum_internet.tex
Cooperative enhancement++

When implementing a quantum computation characterised by completely general computational scaling functions\index{Computational scaling functions}, $f^{X,Y}_\mathrm{sc}$ (which in general can be distinct for the two players $X$ and $Y$), elements in the payoff matrix associated with unification will be enhanced to \mbox{$(c_X,c_Y)$}, where,
\begin{align}
c_X &= \frac{n_X\cdot f^X_\mathrm{sc}(n_X+n_Y)}{n_X+n_Y},\nonumber\\
c_Y &= \frac{n_Y\cdot f^Y_\mathrm{sc}(n_X+n_Y)}{n_X+n_Y},
\end{align}
where the payoff matrix elements are assumed to be in units of classical-equivalent processing time, and resource sharing is based on the techniques for arbitrage-free time-share allocation presented in Sec.~\ref{sec:arb_free_time_share}.

>>>>

When implementing a quantum computation characterised by completely general computational scaling functions\index{Computational scaling functions}, $f^{X,Y}_\mathrm{sc}$ (which in general can be distinct for the two players $X$ and $Y$), elements in the payoff matrix associated with unification will undergo the quantum utility payoff enhancement,
\begin{align}
(f^X_\mathrm{sc}(n_X),f^Y_\mathrm{sc}(n_Y))	\underset{\textsc{Unify}}{\longrightarrow} (c_X,c_Y),
\end{align}
where,
\begin{align}
c_X &= \frac{n_X\cdot f^X_\mathrm{sc}(n_X+n_Y)}{n_X+n_Y},\nonumber\\
c_Y &= \frac{n_Y\cdot f^Y_\mathrm{sc}(n_X+n_Y)}{n_X+n_Y},
\end{align}
and payoff matrix elements are assumed to be in units of classical-equivalent processing time (e.g FLOPs), and resource sharing is based on the methodology for arbitrage-free time-share allocation presented in Sec.~\ref{sec:arb_free_time_share}.
